Supplementary Materials - Needle in a haystack, the pollen dataset

### 2020-09-22 supp-materials/supp-pollen.Rmd
reorder supp materials

<img src="gifs/pollen_sage.gif" width="300"/> <img src="gifs/pollen_sage_R1.gif" width="300"/> <img src="gifs/pollen_sage_gam20.gif" width="300"/>

>>>>

<img src="../gifs/pollen_sage.gif" width="300"/> <img src="../gifs/pollen_sage_R1.gif" width="300"/> <img src="../gifs/pollen_sage_gam20.gif" width="300"/>
